### 2023-02-13 article.tex
Remove comments
Move definitions to supmat

\begin{table}[h]
  \begin{tabular}{lp{5cm}p{5cm}}
    Term         & Definition                                                                   & Example                                                         \\
    \hline
    Code         & Body of text to be run by a computer                                         & The scripts run by a computational experiment                   \\
    Data         & Individual facts, statistics, or items of information                        & The name of a SNP known to have a significant association       \\
    Genotype     & The DNA allele at a certain location                                         & AA, AC, CG, GT, ...                                             \\
    Paradata     & Data that describe the process of generating data                            & The code to conclude that a SNP has a significant association   \\
    Phenotype    & How an organism looks like in the broadest sense                             & The concentration of IL6RA in the blood                         \\
    Primary data & Data that is the foundation of an experiment                                 & The genotype of individuals                                     \\
    Metadata     & Data that provide information about other data                               & The article that describes an experiment                        \\
    Raw data     & Data directly from the real world, that are not yet ready to be primary data & The raw results of getting the genotypes of individuals         \\
    SNP          & A named location within a genome                                             & \verb|rs12133641|                                               \\
    Trait        & A phenotype                                                                  & The concentration of IL6RA in the blood                         
  \end{tabular}
  \caption{Terms used in this paper, and their definitions}
  \label{tab:definitions}
\end{table}

@@

Genetic epidemiology is a field within biology that
tries to determine the spread of heritable traits 
and their underlying biological mechanism.
For example, we know that lactose intolerance in adults is
caused by a decline in the production of lactose-degrading enzymes,
and is most commonly found in south-east Asia and south Africa \cite{storhaug2017country}.
The trait is caused by the genetic make-up, or 'genotype'
(see Table \ref{tab:definitions} for the definitions of terms used in this paper), 
of a person.
The trait, also called 'phenotype' (again, see Table \ref{tab:definitions}), 
in this example is lactose intolerance at adult age,
yet any human property, such as weight or height can be studied.
When an association between genotype and phenotype is found,
these associations, when relevant enough, are used to 
create so-called 'gene panels', 
where the location of the gene causing 
an association is measured specifically, 
to detect people at risk for the associated phenotype.
The rest of this section describes a genetic epidemiology study 
in more detail, with special focus on the computational experiment.

@@

% Duran et al., grounds for trust
% [A] process is epistemically opaque relative to a cognitive agent X at time t
% just in case X does not know at t all of the epistemically relevant elements of
% the process (Humphreys 2009, 618)
% 
% On Computational reliability
% 
% (CR) if S’s believing p at t results from m, then S’s belief in p at t is justified.
% where S is a cognitive agent, p is any truth-valued proposition related to the
% results of a computer simulation, t is any given time, and m is a reliable com‑
% puter simulation.
%
%
% 4 Sources for Computational Reliabilism
%
% 1. Verification and validation methods
% 2. Robustness analysis for computer simulations
% 3. A history of (un)successful implementations
% 4. Expert knowledge

>>>>

@@

Genetic epidemiology is a field within biology that
tries to determine the spread of heritable traits 
and their underlying biological mechanism.
For example, we know that lactose intolerance in adults is
caused by a decline in the production of lactose-degrading enzymes,
and is most commonly found in south-east Asia and south Africa \cite{storhaug2017country}.
The trait is caused by the genetic make-up, or 'genotype'
(see Table \ref{tab:definitions} in the Supplementary Materials
for the definitions of terms used in this paper), of a person.
The trait, also called 'phenotype', 
in this example is lactose intolerance at adult age,
yet any human property, such as weight or height can be studied.
When an association between genotype and phenotype is found,
these associations, when relevant enough, are used to 
create so-called 'gene panels', 
where the location of the gene causing 
an association is measured specifically, 
to detect people at risk for the associated phenotype.
The rest of this section describes a genetic epidemiology study 
in more detail, with special focus on the computational experiment.

@@

\begin{table}[h]
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Term         & Definition                                                                   & Example                                                         \\
    \hline
    Code         & Body of text to be run by a computer                                         & The scripts run by a computational experiment                   \\
    Data         & Individual facts, statistics, or items of information                        & The name of a SNP known to have a significant association       \\
    Genotype     & The DNA allele at a certain location                                         & AA, AC, CG, GT, ...                                             \\
    Paradata     & Data that describe the process of generating data                            & The code to conclude that a SNP has a significant association   \\
    Phenotype    & How an organism looks like in the broadest sense                             & The concentration of IL6RA in the blood                         \\
    Primary data & Data that is the foundation of an experiment                                 & The genotype of individuals                                     \\
    Metadata     & Data that provide information about other data                               & The article that describes an experiment                        \\
    Raw data     & Data directly from the real world, that are not yet ready to be primary data & The raw results of getting the genotypes of individuals         \\
    SNP          & A named location within a genome                                             & \verb|rs12133641|                                               \\
    Trait        & A phenotype                                                                  & The concentration of IL6RA in the blood                         
    \hline
  \end{tabular}
  \caption{Terms used in this paper, and their definitions}
  \label{tab:definitions}
\end{table}
